Spontaneous Similarity Judgments of Musical Tones played with various Playing Techniques

### 2017-12-14 paper/lagrangeSpontaneousSimilarity2017.tex
addition of experiment

Indeed, if the properties of the first processing stages of the human auditory system can reasonably be considered as similar for every subjects despite potential hearing losses for some, the later ones is expected to vary more drastically due to his education, tastes and experiences with stimuli similar to the \ipt that are considered in this study.

>>>>

Indeed, if the properties of the first processing stages of the human auditory system can reasonably be considered as similar for every subjects despite potential hearing losses for some, the later ones is expected to vary more drastically due to their respective education, tastes and experiences with stimuli similar to the \ipt that are considered in this study. We therefore consider a supervised setting in order to optimize the representational space provided by the scattering transform.

To do so, several
